Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-02-15 numerical-timestep.tex
Finished seciton on timesteps.

\begin{equation}
\Delta t_{cond} = min \left(  \kappa_{cond} \frac{\Delta x^2
    n}{\kappa(T)} \right)_L,
\label{eqn:dtcond}
\end{equation}

@@

Equation~\ref{}

>>>>

\begin{equation}
\Delta t_{cond} = min \left(  \frac{ \kappa_{cond}}{f_{Sp}} \frac{\Delta x^2
    n_b}{\kappa(T)} \right)_L,
\label{eqn:dtcond}
\end{equation}

@@

Equation~\ref{eqn:dtcond} is the CFL condition for an explicit
solution to the equation of heat conduction.  In this expression,
$n_b$ is the baryon number density, defined as $n_b = \rho_b / \mu
m_p$, where $\mu$ is the mean molecular weight, $\kappa(T)$ is the
Spitzer thermal conductivity, and f$_{Sp}$ is a user-defined
conduction suppression factor whose value must be f$_{Sp} \leq 1$.  Both are defined in
Section~\ref{sec.num.conductions}.  \kappa_{cond} is a prefactor whose
value must be $0 < \kappa_{cond}  < 0.5$, and is exactly 0.5 for the
implemention in Enzo.
From a practical
perspective, it is useful to note that, unlike other timestep criteria
discussed above (which effectively scale as $\Delta x / \sqrt{T}$,
the timestep criterion due to thermal conduction scales as $\Delta x^2
/ T^{2.5}$, which can result in a rapid decrease in timestep in
regions of high resolution and/or temperature.

Finally, Equation~\ref{eqn:dtexpand} is a cosmological constraint that
limits the timestep so that the simulated universe only expands by
some fractional amount, f$_{exp}$, during a single step.  In this
equation, $a$ and $\dot{a}$ refer to the scale factor of the universe
and its rate of change, respectively.  This
criteria is necessary because the expansion of the universe and its
first derivative with respect to time both appear in the equations of cosmological (magneto)hydrodynamics and particle motion,
and some limit is required in order to model the change of energy and
momentum due to expansion with a reasonable level of accuracy.  In
reality, this is only a significant limitation at very high redshift;
at later times, other timestep criteria are much more important.
